---
title: "분기별 선형모형"
date: "2023/10/26"
author: "Sungil Park"
description: "2023-2학기 R로 하는 금융데이터분석"
---

```{r, include=FALSE}
rm(list=ls())
library(tidyverse)
library(knitr)
library(highcharter)
```

## Data

```{r}
data_bin <- readxl::read_xlsx("contents/2. 예측수준의 결정.xlsx",sheet = 2)
data_sim <- readxl::read_xlsx("contents/2. 예측수준의 결정.xlsx",sheet = 3)

data_bin %>% head() %>% kable()
```


```{r, include=FALSE}
lm(in1_bin ~ t, data = filter(data_bin,data_bin$quat == 1)) %>% summary()
lm(in1_bin ~ t, data = filter(data_bin,data_bin$quat == 2)) %>% summary()
lm(in1_bin ~ t, data = filter(data_bin,data_bin$quat == 3)) %>% summary()
lm(in1_bin ~ t, data = filter(data_bin,data_bin$quat == 4)) %>% summary()
```

## 분기별 선형모형

### in1_bin

```{r}
data_bin %>% ggplot(aes(x=t, y=in1_bin, color = factor(quat)))+
  geom_point()+
  geom_smooth(data = data_bin,aes(x=t,y=in1_bin,color = factor(quat)),method = "lm",se=FALSE)+
  theme_minimal()
```

#### 1분기
 
$$
y = 5.58161 + 0.08196 * t
$$

 - R-squared :

```{r, echo=FALSE}
summary(lm(in1_bin ~ t, data = filter(data_bin,quat == 1)))$r.squared
```
 - adj R-squared :

```{r, echo=FALSE}
summary(lm(in1_bin ~ t, data = filter(data_bin,quat == 1)))$adj.r.squared
```
 - p-value :

```{r, echo=FALSE}
summary(lm(in1_bin ~ t, data = filter(data_bin,quat == 1)))$coefficients["t", "Pr(>|t|)"]
```
#### 2분기
 
$$
y = 5.69036 + 0.08661 * t
$$

 - R-squared :

```{r, echo=FALSE}
summary(lm(in1_bin ~ t, data = filter(data_bin,quat == 2)))$r.squared
```
 - adj R-squared :

```{r, echo=FALSE}
summary(lm(in1_bin ~ t, data = filter(data_bin,quat == 2)))$adj.r.squared
```
 - p-value :

```{r, echo=FALSE}
summary(lm(in1_bin ~ t, data = filter(data_bin,quat == 2)))$coefficients["t", "Pr(>|t|)"]
```

#### 3분기
 
$$
y = 5.98027 + 0.09741 * t
$$

 - R-squared :

```{r, echo=FALSE}
summary(lm(in1_bin ~ t, data = filter(data_bin,quat == 3)))$r.squared
```
 - adj R-squared :

```{r, echo=FALSE}
summary(lm(in1_bin ~ t, data = filter(data_bin,quat == 3)))$adj.r.squared
```
 - p-value :

```{r, echo=FALSE}
summary(lm(in1_bin ~ t, data = filter(data_bin,quat == 3)))$coefficients["t", "Pr(>|t|)"]
```


#### 4분기
 
$$
y = 6.02714 + 0.9991 * t
$$



 - R-squared :

```{r, echo=FALSE}
summary(lm(in1_bin ~ t, data = filter(data_bin,quat == 4)))$r.squared
```
 - adj R-squared :

```{r, echo=FALSE}
summary(lm(in1_bin ~ t, data = filter(data_bin,quat == 4)))$adj.r.squared
```
 - p-value :

```{r, echo=FALSE}
summary(lm(in1_bin ~ t, data = filter(data_bin,quat == 4)))$coefficients["t", "Pr(>|t|)"]
```



### mul_bin

```{r}
data_bin %>% ggplot(aes(x=t, y=mul_bin, color = factor(quat)))+
  geom_point()+
  geom_smooth(data = data_bin,aes(x=t,y=mul_bin,color = factor(quat)),method = "lm",se=FALSE)+
  theme_minimal()
```

#### 1분기
 

 - R-squared :

```{r, echo=FALSE}
summary(lm(mul_bin ~ t, data = filter(data_bin,quat == 1)))$r.squared
```
 - adj R-squared :

```{r, echo=FALSE}
summary(lm(mul_bin ~ t, data = filter(data_bin,quat == 1)))$adj.r.squared
```
 - p-value :

```{r, echo=FALSE}
summary(lm(mul_bin ~ t, data = filter(data_bin,quat == 1)))$coefficients["t", "Pr(>|t|)"]
```
#### 2분기
 

 - R-squared :

```{r, echo=FALSE}
summary(lm(mul_bin ~ t, data = filter(data_bin,quat == 2)))$r.squared
```
 - adj R-squared :

```{r, echo=FALSE}
summary(lm(mul_bin ~ t, data = filter(data_bin,quat == 2)))$adj.r.squared
```
 - p-value :

```{r, echo=FALSE}
summary(lm(mul_bin ~ t, data = filter(data_bin,quat == 2)))$coefficients["t", "Pr(>|t|)"]
```

#### 3분기
 
 - R-squared :

```{r, echo=FALSE}
summary(lm(mul_bin ~ t, data = filter(data_bin,quat == 3)))$r.squared
```
 - adj R-squared :

```{r, echo=FALSE}
summary(lm(mul_bin ~ t, data = filter(data_bin,quat == 3)))$adj.r.squared
```
 - p-value :

```{r, echo=FALSE}
summary(lm(mul_bin ~ t, data = filter(data_bin,quat == 3)))$coefficients["t", "Pr(>|t|)"]
```


#### 4분기

 - R-squared :

```{r, echo=FALSE}
summary(lm(mul_bin ~ t, data = filter(data_bin,quat == 4)))$r.squared
```
 - adj R-squared :

```{r, echo=FALSE}
summary(lm(mul_bin ~ t, data = filter(data_bin,quat == 4)))$adj.r.squared
```
 - p-value :

```{r, echo=FALSE}
summary(lm(mul_bin ~ t, data = filter(data_bin,quat == 4)))$coefficients["t", "Pr(>|t|)"]
```

### jas_bin

```{r}
data_bin %>% ggplot(aes(x=t, y=jas_bin, color = factor(quat)))+
  geom_point()+
  geom_smooth(data = data_bin,aes(x=t,y=jas_bin,color = factor(quat)),method = "lm",se=FALSE)+
  theme_minimal()
```

#### 1분기
 

 - R-squared :

```{r, echo=FALSE}
summary(lm(jas_bin ~ t, data = filter(data_bin,quat == 1)))$r.squared
```
 - adj R-squared :

```{r, echo=FALSE}
summary(lm(jas_bin ~ t, data = filter(data_bin,quat == 1)))$adj.r.squared
```
 - p-value :

```{r, echo=FALSE}
summary(lm(jas_bin ~ t, data = filter(data_bin,quat == 1)))$coefficients["t", "Pr(>|t|)"]
```
#### 2분기
 

 - R-squared :

```{r, echo=FALSE}
summary(lm(jas_bin ~ t, data = filter(data_bin,quat == 2)))$r.squared
```
 - adj R-squared :

```{r, echo=FALSE}
summary(lm(jas_bin ~ t, data = filter(data_bin,quat == 2)))$adj.r.squared
```
 - p-value :

```{r, echo=FALSE}
summary(lm(jas_bin ~ t, data = filter(data_bin,quat == 2)))$coefficients["t", "Pr(>|t|)"]
```

#### 3분기
 
 - R-squared :

```{r, echo=FALSE}
summary(lm(jas_bin ~ t, data = filter(data_bin,quat == 3)))$r.squared
```
 - adj R-squared :

```{r, echo=FALSE}
summary(lm(jas_bin ~ t, data = filter(data_bin,quat == 3)))$adj.r.squared
```
 - p-value :

```{r, echo=FALSE}
summary(lm(jas_bin ~ t, data = filter(data_bin,quat == 3)))$coefficients["t", "Pr(>|t|)"]
```


#### 4분기

 - R-squared :

```{r, echo=FALSE}
summary(lm(jas_bin ~ t, data = filter(data_bin,quat == 4)))$r.squared
```
 - adj R-squared :

```{r, echo=FALSE}
summary(lm(jas_bin ~ t, data = filter(data_bin,quat == 4)))$adj.r.squared
```
 - p-value :

```{r, echo=FALSE}
summary(lm(jas_bin ~ t, data = filter(data_bin,quat == 4)))$coefficients["t", "Pr(>|t|)"]
```



### cha_bin

```{r}
data_bin %>% ggplot(aes(x=t, y=cha_bin, color = factor(quat)))+
  geom_point()+
  geom_smooth(data = data_bin,aes(x=t,y=cha_bin,color = factor(quat)),method = "lm",se=FALSE)+
  theme_minimal()
```

#### 1분기
 

 - R-squared :

```{r, echo=FALSE}
summary(lm(cha_bin ~ t, data = filter(data_bin,quat == 1)))$r.squared
```
 - adj R-squared :

```{r, echo=FALSE}
summary(lm(cha_bin ~ t, data = filter(data_bin,quat == 1)))$adj.r.squared
```
 - p-value :

```{r, echo=FALSE}
summary(lm(cha_bin ~ t, data = filter(data_bin,quat == 1)))$coefficients["t", "Pr(>|t|)"]
```
#### 2분기
 

 - R-squared :

```{r, echo=FALSE}
summary(lm(cha_bin ~ t, data = filter(data_bin,quat == 2)))$r.squared
```
 - adj R-squared :

```{r, echo=FALSE}
summary(lm(cha_bin ~ t, data = filter(data_bin,quat == 2)))$adj.r.squared
```
 - p-value :

```{r, echo=FALSE}
summary(lm(cha_bin ~ t, data = filter(data_bin,quat == 2)))$coefficients["t", "Pr(>|t|)"]
```

#### 3분기
 
 - R-squared :

```{r, echo=FALSE}
summary(lm(cha_bin ~ t, data = filter(data_bin,quat == 3)))$r.squared
```
 - adj R-squared :

```{r, echo=FALSE}
summary(lm(cha_bin ~ t, data = filter(data_bin,quat == 3)))$adj.r.squared
```
 - p-value :

```{r, echo=FALSE}
summary(lm(cha_bin ~ t, data = filter(data_bin,quat == 3)))$coefficients["t", "Pr(>|t|)"]
```


#### 4분기

 - R-squared :

```{r, echo=FALSE}
summary(lm(cha_bin ~ t, data = filter(data_bin,quat == 4)))$r.squared
```
 - adj R-squared :

```{r, echo=FALSE}
summary(lm(cha_bin ~ t, data = filter(data_bin,quat == 4)))$adj.r.squared
```
 - p-value :

```{r, echo=FALSE}
summary(lm(cha_bin ~ t, data = filter(data_bin,quat == 4)))$coefficients["t", "Pr(>|t|)"]
```


